---
title: "The 'GermaNER'-package"
author: "Andreas Blätte (andreas.blaette@uni-due.de)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: bibliography.bibtex
vignette: >
  %\VignetteIndexEntry{The GermaNER-package}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

## About GermaNER

See [@Benikova2015]!


## Getting Named Entities

```{r load_packages}
library(GermaNER)
library(polmineR)
library(magrittr)
library(cwbtools)
```

```{r get_germaner}
if (!file.exists(germaner_jar_filename())) germaner_download_jar()
```

```{r create_subcorpus}
am <- corpus("GERMAPARLMINI") %>%
  subset(speaker == "Angela Dorothea Merkel" & date == "2009-11-10")
```

```{r get_named_entities}
am_ne <- germaner_get_named_entities(am)
```

The resulting `data.frame` follows ConLL conventions.

```{r ne_show_head}
head(am_ne)
```


## Encoding Named Entities

Using the `conll_get_regions` function, we can get the regions.

```{r get_regions}
ne_regions <- conll_get_regions(am_ne)
```


```{r inspect_regions}
head(ne_regions)
```

```{r copy_corpus, eval = FALSE}
corpus_copy(
  corpus = "GERMAPARLMINI", registry_dir = registry(),
  verbose = interactive(), progress = interactive()
)
```

```{r encode_ne}
s_attribute_encode(
  values = ne_regions[["ne_type"]],
  data_dir = cwbtools::registry_file_parse(corpus = "GERMAPARLMINI")[["home"]],
  s_attribute = "ne",
  corpus = "GERMAPARLMINI",
  region_matrix = as.matrix(ne_regions[, c("cpos_left", "cpos_right")]),
  method = "R",
  registry_dir = Sys.getenv("CORPUS_REGISTRY"),
  encoding = "UTF-8",
  delete = TRUE,
  verbose = TRUE
)
```

```{r inspect_s_attributes}
s_attributes("GERMAPARLMINI")
```


```{r inspect_s_attribute_values}
s_attributes("GERMAPARLMINI", "ne")
```


## Checking structural annotation of named entities

### Initial tests

A first test is whether we can create a subcorpus with the newly annotated regions

```{r create_ne_subcorpus}
corpus("GERMAPARLMINI") %>% subset(grepl("^.*$", ne))
```

Should be identical with the regions in the table!

```{r check_ne_subcorpus_size}
sum(ne_regions[["cpos_right"]] - ne_regions[["cpos_left"]]) + nrow(ne_regions)
```

```{r}
registry_reset()
```


### Counting

```{r ne_count}
count("GERMAPARLMINI", query = '/region[ne]', cqp = TRUE)
count("GERMAPARLMINI", query = '/region[ne,a]::a.ne="ORG"', cqp = TRUE)
count("GERMAPARLMINI", query = '/region[ne,a]::a.ne="PER"', cqp = TRUE)
count("GERMAPARLMINI", query = '/region[ne,a]::a.ne="LOC"', cqp = TRUE)
count("GERMAPARLMINI", query = '/region[ne,a]::a.ne="OTH"', cqp = TRUE)
```


### Keywords-in-context

```{r kwic_all_ne, render = knit_print}
kwic("GERMAPARLMINI", query = '<ne> []* </ne>', cqp = TRUE)
```

```{r kwic_all_ne_alternative_cqp_syntax, render = knit_print}
kwic("GERMAPARLMINI", query = '/region[ne]', cqp = TRUE)
```

```{r kwic_ne_persons, render = knit_print}
kwic("GERMAPARLMINI", query = '/region[ne,a]::a.ne="PER";', cqp = TRUE)
```


```{r kwic_ne_organisations, render = knit_print}
kwic("GERMAPARLMINI", query = '/region[ne,a]::a.ne="ORG";', cqp = TRUE)
```


```{r kwic_ne_locations, render = knit_print}
kwic("GERMAPARLMINI", query = '/region[ne,a]::a.ne="LOC";', cqp = TRUE)
```



## Bibliography